Stack Safety as a Security Property

### 2020-07-08 main.tex
Tackle problematic paragraph in intro

\bcp{Again, here, a bigger transition, more setup, and a longer discussion
  are needed.  This is really the crux of what we are doing!}
Moreover, applying the standard language-based-security notions of
integrity and confidentiality in the stack-safety setting raises a novel
challenge:
the notion of ``attacker'' changes during execution. Not only does a
caller need to be protected from its callee, but the callee itself
needs to be protected from {\em its} callees. We address this
challenge by adjusting the integrity and confidentiality of different
stack frames at each call or return transition between
functions.  \bcp{that's way too terse!}
%\apt{connection to ``attacker'' still vague.}  \rb{Mention
%  to varying ``accessing power'' of the attacker?  The notion of
%  attacker changes on certain actions that are not externally
%  visible.} \bcp{Maybe the best way is to grab the bull by the horns:
%  ``If we're going to phrase stack safety as a security property, we
%  need to talk about an attacker model, and this is where the
%  technicalities get really interesting...''}

>>>>

Adopting that model, however, poses another novel challege: not only
does a caller need to be protected from its callee, but the callee
itself needs to be protected from {\em its} callees: the notion of
``attacker'' changes throughout the execution of a program!

\bcp{Again, here, a bigger transition, more setup, and a longer
  discussion are needed.  This is really the crux of what we are
  doing!} \leo{Attempt}
%
Moreover, applying the standard language-based-security notions of
integrity and confidentiality in the stack-safety setting raises a
novel challenge: the notion of ``attacker'' changes during execution.
Not only does a caller need to be protected from its callee, but the
callee itself needs to be protected from {\em its} callees. We address
this problem by using a similarly changing notion of accessibility for
the different components of the machine: we adjust the integrity and
confidentiality level of different stack locations and registers at
every transition (call or return) between functions.  \bcp{that's way too
  terse!}\leo{Slightly better, still needs a bit probably}
%\apt{connection to ``attacker'' still vague.}  \rb{Mention
%  to varying ``accessing power'' of the attacker?  The notion of
%  attacker changes on certain actions that are not externally
%  visible.} \bcp{Maybe the best way is to grab the bull by the horns:
%  ``If we're going to phrase stack safety as a security property, we
%  need to talk about an attacker model, and this is where the
%  technicalities get really interesting...''}
